Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-07-04 papers/paper/paper.tex
Added pdf to run fac

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
\caption[Stepping statistics of model]{\textbf{Stepping statistics of model.} \textit{Top: } Heatmap of initial foot displacement vs. step length. Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place. Step length defined as final displacement minus initial displacement. Linear regression calculated in orange, compared with Yildiz's linear regression plotted in red. Contours of 90\%, 50\%, 25\%, and 5\% displayed as white lines. \textit{Bottom: } Probability density of model step sizes plotted against Yildiz's distribution of step sizes. }
\label{fig:SteppingPlots}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking. Red and blue labeled heads shows independence from each other during processive walking. Experimentalal trace from \cite{Dewitt2012} offset by 120 nm to display comparison. Average velocity of 26 nm/s for both traces.}
	\label{fig:TrajPlot}
\end{figure}

>>>>

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_probability_distribution_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
\includegraphics[width=1\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
\caption[Stepping statistics of model]{\textbf{Stepping statistics of model.} \textit{Top: } Heatmap of initial foot displacement vs. step length. Initial displacement defined as position of the stepping MTBD minus the position of the stationary MTBD, before the step takes place. Step length defined as final displacement minus initial displacement. Linear regression calculated in orange, compared with Yildiz's linear regression plotted in red. Contours of 90\%, 50\%, 25\%, and 5\% displayed as white lines. \textit{Bottom: } Probability density of model step sizes plotted against Yildiz's distribution of step sizes. }
\label{fig:SteppingPlots}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.5_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.35}
	\caption[Stepping trace of head labeled dynein]{\textbf{Stepping trace of head labeled dynein.} Trajectory of MTBD over 24 seconds of walking. Red and blue labeled heads shows independence from each other during processive walking. Experimentalal trace from \cite{Dewitt2012} offset by 120 nm to display comparison. Average velocity of 26 nm/s for both traces.}
	\label{fig:TrajPlot}
\end{figure}
